\documentclass[11pt,a4paper]{article}

%=== Packages ===%
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{hyperref}

%=== Document ===%
\begin{document}

\begin{flushright}
\textbf{David Armando Ramírez Navarrete} \\
Mexico City, Mexico \\
\href{mailto:navarreteram.david@gmail.com}{navarreteram.david@gmail.com} \\
+52 5665840175 \\
\href{https://www.linkedin.com}{LinkedIn} \quad | \quad \href{https://www.github.com}{GitHub}
\end{flushright}

\vspace{1cm}

\begin{flushleft}
\textbf{Hiring Manager} \\
NielsenIQ (NIQ) \\
\end{flushleft}

\vspace{0.5cm}

\textbf{Dear Hiring Manager,}

I am writing to express my enthusiasm for the Data Scientist position at NielsenIQ. After reviewing the role, I am confident that my background in data analysis, automation, and machine learning aligns closely with the qualities you seek in candidates who will contribute to NIQ's innovative and data-driven mission. As a Systems Engineer specializing in Data Science and Machine Learning, I am eager to apply my analytical skills and technical training to support the development of insights that measure and explain consumer behavior.

During my professional experience at NTT DATA, I strengthened my analytical and problem-solving abilities by working with production systems, conducting data-driven evaluations, and automating processes to improve operational efficiency. I routinely leveraged tools such as Python, SQL, Looker Studio, and Bash to create automations, monitor deployments, and perform error analysis—experiences that translate naturally into the role's emphasis on exploring datasets, generating summaries, and building automated solutions.

My academic and project background further complements the technical and statistical foundations required for the role. I have developed machine learning pipelines, implemented deep learning models using TensorFlow and Keras, and applied data preprocessing, balancing, and model optimization techniques. These experiences reflect my curiosity, commitment to continuous learning, and ability to communicate complex concepts clearly to technical and non-technical stakeholders alike.
What excites me most about NielsenIQ is its global impact and dedication to innovation. The opportunity to collaborate with multidisciplinary data science teams while contributing to products that influence decision-making across markets aligns perfectly with my professional goals. I am particularly motivated by NIQ’s emphasis on experimentation, automation, and the thoughtful application of statistical methodologies.

I am confident that my blend of technical expertise, analytical mindset, and passion for learning will allow me to add value to your team. I would welcome the opportunity to discuss how my background and motivation align with the goals of NIQ.

Thank you very much for your time and consideration.

\vspace{0.5cm}

Sincerely, \\
\textbf{David Armando Ramírez Navarrete}

\end{document}
